Software Citation Principles

### 2016-03-21 sc-principles/software-citation-principles.tex
incorporating Arfon's comment - in Intro

These software citation principles were originally based on an adaptation of the FORCE11 Data Citation Principles~\cite{data-citation-principles}, and then were modified based on working group discussions and the information from the use cases and the related work.
The adaptations and modifications have been made because software, while similar to data in terms of not traditionally having been cited in publications, is also different than data in that it can be used to express or explain concepts and it is executable.  \katznote{are there any other difference between software and data that should be stated here?} \asnote{...and is likely updated more frequently? (I don't have a reference for this statement)}  Also, while software can be considered a type of data, the converse is not generally true.

>>>>

These software citation principles were originally based on an adaptation of the FORCE11 Data Citation Principles~\cite{data-citation-principles}, and then were modified based on working group discussions and the information from the use cases and the related work.
The adaptations and modifications have been made because software, while similar to data in terms of not traditionally having been cited in publications, is also different than data in that it can be used to express or explain concepts, it is updated more frequently, and it is executable.  \katznote{are there any other difference between software and data that should be stated here?}  Also, while software can be considered a type of data, the converse is not generally true.
